---
title: "Cat~Numerical template"
author: "Dr K"
date: "November 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# t.test

This is a template to serve as an example (cut and paste, change variable names)  
we use the ucdavis1 dataset from the tigerstats package.

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
data(ucdavis1)
davisdata <- na.omit(ucdavis1)
```


###Plot boxplots

```{r}
plot(momheight~Sex,data=davisdata)
```

##Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(ucdavis1,aes(x=Sex,y=dadheight))
```
##Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
###get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

# Numerical results

```{r}
favstats(momheight~Sex,data=ucdavis1)
```

# Inferential  
  
```{r}
t.test(momheight~Sex,data=ucdavis1)
```
# One Way Anova
  
  

###Plot boxplots

```{r}
plot(alcohol~Seat,data=davisdata)
```
   
####Using ggplot

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```
  
# Numerical results

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
# Inferential

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

##When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

